A UK Case Study on\\Cybersecurity Education and Accreditation

### 2019-07-24 FIE2019-final.tex
Changes to Intro

Cybersecurity has increasingly been a headline feature in the news over recent years, generally prompted by spectacular breaches, from major credit reference agencies~\cite{equifax2017}, telecoms companies~\cite{talktalk2016}, national airlines~\cite{BritishAirways2018a}, online dating websites~\cite{ashleymadison2015}, and even between sovereign governments~\cite{ncsc2018}. These major breaches have had significant impact on both individual citizens and society in general, requiring attention from organisations of all sizes~\cite{Hannigan2019a}\footnote{Former Director of GCHQ: UK equivalent of NSA.}:
\begin{quote}
``{\emph{...[need to] change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''
\end{quote}
\noindent
These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and largely driven by training materials, which makes it harder to establish a common body of knowledge (for example, in the UK, the CyBOK project~\cite{Bristol2019a} is still a work in progress). An international perspective is harder still, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are free to conceptualise, design, package and market their initiatives, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent or ambition of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as post-compulsory -- to respond to this situation, at the individual level and via recommended curricula~\cite{mcgettrick-et-al:sigcse2014,ACM2017b} and professional accreditation requirements~\cite{BCS2018a}. This is further reinforced by a wider focus on digital skills and computer science education reform, especially across the nations of the UK~\cite{brown-et-al:toce2014,murphy-et-al:programming2017,tryfonas+crick:petra2018}.

A recent ACM working group, as part of the Innovation and Technology in Computer Science Education (ITiCSE) conference series~\cite{Parrishetal2018a}, has been capturing global perspectives on cybersecurity education, but has yet to report its full findings. An aim of the ITiCSE working group is to develop a taxonomy for approaches to cybersecurity education, resulting in improved standards and goals for many different types of cybersecurity programmes; a further aim is to ``catalog existing [\dots] knowledge materials'', but there is no mention of any quality control over these. Nevertheless, it is one thing to write national curricula, specifications and requirements, and another thing to deliver appropriate and relevant education and skills; furthermore, this paper asks how well this is done in practice.

@@

The NCSC is a UK Government organisation tasked with enhancing the cybersecurity of the UK. The NCSC publishes and accredits to a number of cybersecurity standards \cite{NCSC2018a}. These standards are linked to the ACM recommendations for curricula \cite{ACM2013a}. To date the major focus of NCSC accreditation has been upon Masters degrees specialising in cybersecurity. More recently the NCSC has also began accrediting integrative masters programmes, undergraduate degrees in cybersecurity and computer science degrees with a significant cybersecurity focus \cite{NCSC2018b}.

>>>>

Cybersecurity has increasingly been a headline feature in the news over recent years, generally prompted by spectacular breaches, including major credit reference agencies~\cite{equifax2017}, telecoms companies~\cite{talktalk2016}, national airlines~\cite{BritishAirways2018a}, online dating websites~\cite{ashleymadison2015}, and even between sovereign governments~\cite{ncsc2018}. These major breaches have had significant impact on both individual citizens and society in general, requiring attention from organisations of all sizes:
\begin{quote}
``{\emph{...[need to] change the culture in your organisation around cyber security; to try to do for cyber what has been done so successfully for health and safety, for example, over the last ten years --- to get everybody to take it seriously; to take the risk management process seriously and drive that down through the organisation.}}''\\
Robert Hannigan, former Director of GCHQ~\cite{Hannigan2019a}'
\end{quote}

These global cybersecurity crises have compelled academic institutions to address the demand for educated cybersecurity professionals~\cite{McGettrick2013}. As no shared framework for ``cybersecurity'' as an academic discipline exists, growth has been unfocused and largely driven by training materials, which makes it harder to establish a common body of knowledge (for example, in the UK, the CyBOK project~\cite{Bristol2019a} is still a work in progress). An international perspective is harder still, as different nations use different criteria to define local needs~\cite{schneider2013}. As a result, new programmes entering this space are free to conceptualise, design, package and market their initiatives, as there is no globally accepted reference model for cybersecurity to allow employers or students to understand the extent or ambition of a given cybersecurity program~\cite{conklin-et-al:2014,Parrishetal2018a}.

With this significant economic and societal focus on cybersecurity, there are calls for formal education -- school-level as well as tertiary -- to respond to this situation, at the individual level and via recommended curricula~\cite{mcgettrick-et-al:sigcse2014,ACM2017b} and professional accreditation requirements~\cite{BCS2018a,NCSC2017}. This is further reinforced by a wider focus on digital skills and computer science education reform, especially across the nations of the UK~\cite{brown-et-al:toce2014,murphy-et-al:programming2017,tryfonas+crick:petra2018}.

A recent ACM working group~\cite{Parrishetal2018a}, as part of the {\emph{Innovation and Technology in Computer Science Education}} (ITiCSE) conference series, has been capturing global perspectives on cybersecurity education, but as of July 2019 has yet to report its full findings. An aim of the ITiCSE working group is to develop a taxonomy for approaches to cybersecurity education, resulting in improved standards and goals for many different types of cybersecurity programmes; a further aim is to ``{\emph{catalog existing [\dots] knowledge materials}}'', but there is no mention of any quality control over these. Nevertheless, it is one thing to write national curricula, specifications and requirements, and another thing to deliver appropriate and relevant education and skills; this paper asks how well this is done in practice.

@@

The NCSC is a UK Government organisation tasked with enhancing the cybersecurity of the UK. The NCSC publishes and accredits to a number of cybersecurity standards~\cite{NCSC2017}. These standards are linked to the ACM recommendations for curricula \cite{ACM2013a}. To date the major focus of NCSC accreditation has been upon Masters degrees specialising in cybersecurity. More recently the NCSC has also began accrediting integrative masters programmes, undergraduate degrees in cybersecurity and computer science degrees with a significant cybersecurity focus \cite{NCSC2018b}.
